---
title: "Lecture 2 Example: Data Import"
output: github_document
---

Loading this package because it has tools we need.
```{r setup}
library(tidyverse)
```

## Read in some data. 
If you click in the data using file>read-in etc. you are not doing something reproducible, this is why it is better if it exists in your code. 

Absolute directions give the very first documents on your computer. Relative paths are like saying.. "starting from where you are now, take x step" 

```{r}
litters_df = read_csv("./data/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)

```

## Take a look at the data 

```{r}
litters_df
```

```{r}
head(litters_df)

tail(litters_df)
```

```{r}
skimr::skim(litters_df)
```

You can do view() function in the console and it will load the dataset in a separate window. Try to avoid doing it from up here because it might screw up knitting process. 

A dbl is a particular type of number in computer science/programming - we should think of these as numbers. 
