---
title: "Lecture 2 Example: Data Import"
output: github_document
---

Loading this package because it has tools we need.
```{r setup}
library(tidyverse)
```

## Read in some data. 
If you click in the data using file>read-in etc. you are not doing something reproducible, this is why it is better if it exists in your code. 

Absolute directions give the very first documents on your computer. Relative paths are like saying.. "starting from where you are now, take x step" 

```{r}
litters_df = read_csv("./data/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)

```

## Take a look at the data 

```{r}
litters_df
```

```{r}
head(litters_df)

tail(litters_df)
```

```{r}
skimr::skim(litters_df)
```

You can do view() function in the console and it will load the dataset in a separate window. Try to avoid doing it from up here because it might screw up knitting process. 

A dbl is a particular type of number in computer science/programming - we should think of these as numbers. 

CSV stands for comma separated values

##Options to read_csv

This is useful when the csv given to you is strangely structured, maybe a description of the dataset in the first few rows. 
```{r}
litters_df = read_csv("./data/FAS_litters.csv", skip = 10, col_names = FALSE)
litters_df
```

This is a way to draw out missing values however they are stored. You can also do this with ".", 888, or whatever you want. 
```{r}
litters_df = read_csv("./data/FAS_litters.csv", na = c("","NA",999))
litters_df
```

The CSV reader will attempt to define the column variable types, we can define this ourselves as well. 
Check out '?read_csv()' for more information 

